\emph{icepack}: a novel glacier flow modeling package

### 2019-08-15 icepack.tex
More contrast with varglas

The glacier flow modeling package closest in spirit to icepack is VarGlaS \citep{brinkerhoff2013data}.
VarGlaS is implemented using the finite element modeling package FEniCS \citep{logg2012automated}.
The Firedrake project began as an outgrowth of FEniCS and both packages implement the same domain-specific language for specifying weak forms of PDE.
Icepack improves upon the groundwork laid in VarGlaS through its use of tensor product finite elements on extruded meshes, both of which are only available in firedrake \citep{bercea2016structure, mcrae2016automated}.
These two features enable the definition of a much simpler 3D flow model that we will describe in \S\ref{sec:physics-hybrid-model}.

@@

\subsection{Substituting model components}

>>>>

The glacier flow modeling package closest in spirit to icepack is VarGlaS \citep{brinkerhoff2013data}.
VarGlaS is implemented using the finite element modeling package FEniCS \citep{logg2012automated}.
The Firedrake project began as an outgrowth of FEniCS and both packages implement the same domain-specific language for describing weak forms of PDE.
Icepack improves upon the groundwork laid in VarGlaS in three main respects.
First, icepack includes a simple 3D flow model that uses several features only available in firedrake: extruded meshes and tensor product finite elements \citep{bercea2016structure, mcrae2016automated}.
This model will be described in section \S\ref{sec:physics-hybrid-model}.
Second, the inverse solver in icepack uses the Gauss-Newton method, which converges faster and more reliably than the BFGS method used in VarGlaS; see section \S\ref{sec:numerics-inverse-solvers}.
Finally, the architecture of icepack is designed to make it easy for users to modify the components of each model, such as the rheology and basal friction.
The software design that made this possible is discussed in section \S\ref{sec:physics-substitution}.

@@

\subsection{Substituting model components} \label{sec:physics-substitution}
